%-------------------------
% Resume in LaTex
% Author : Dalton Luce
% License : MIT
%------------------------

 % Conditionally include the private information if `private` true
 % To render with private info: pdflatex '\def\private{} \input{cv.tex}'
\ifdefined\private
  \input{.private.tex}
\fi

\newcommand{\addressConditional}{
    \ifdefined\private
        \address
    \else
        Boston, MA
    \fi
    \hspace{10pt}
}
\newcommand{\phoneConditional}{
    \ifdefined\private
        \phone
        \hspace{10pt}
    \fi
}
\newcommand{\emailConditional}{
    \ifdefined\private
        \href{mailto:\email}{\underline{\email}}
        \hspace{10pt}
    \fi
}

\documentclass[letterpaper,8pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-3pt}
    \titlerule\vspace{1pt}\scshape\raggedright\large
}{}{0em}{\vspace{-10pt}}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Use filled circles for bullet points
\renewcommand\labelitemi{\small\textbullet}

\newcommand{\resumeEntry}[4]{
    \vspace{4pt}
    \large \textbf{#1}
    \normalsize \hfill #2
    \\
    \textit{#3} \hfill \textit{#4}
    \vspace{1pt}
}

\newcommand{\itemsBegin}{
    \begin{itemize}[leftmargin=0.2in, labelsep=0.05in, itemsep=0pt, parsep=1pt, topsep=0pt, partopsep=0pt]
}

\newcommand{\itemsEnd}{\end{itemize}}

%-------------------------------------------
% RESUME STARTS HERE

\begin{document}

%----------HEADING----------
\textbf{\huge \scshape Dalton Luce} \\
\vspace{2pt}
\small
% Address
\addressConditional
% Phone
\phoneConditional
% Email
\emailConditional
% LinkedIn
\href{https://www.linkedin.com/in/dalton-luce/}{\underline{LinkedIn}}
\hspace{10pt}
% GitHub
\href{https://github.com/da-luce}{\underline{GitHub}}
\hspace{10pt}
% Portfolio Website
\href{https://daltonluce.com/}{\underline{daltonluce.com}}
\vspace{-5pt}

%-----------EDUCATION-----------
\section{Education}

    %--------Cornell--------
    \resumeEntry
        {Cornell University}
        {Expected 2026}
        {Bachelor of Science in Electrical and Computer Engineering, CS minor}
        {Ithaca, NY}

    \itemsBegin
        \item 4.028 GPA, Dean’s List all semesters
        \item James E. Rice Jr. First Year Writing Seminar Award Nominee
        \item Autobike Project Team Software Lead, IEEE at Cornell Executive Board, Cornell Outdoor Education Student Instructor, Cornell Club Swim
        \item Relevant coursework: Calculus for Engineers; Multivariable Calculus for Engineers; Differential Equations for Engineers; Linear Algebra for Engineers; Physics II: Electromagnetism; Physics III: Oscillations, Waves, and Quantum Physics; Data Structures and Functional Programming; Object-Oriented Programming and Data Structures; Data Science for Engineers; Digital Logic and Computer Organization; Embedded Systems
    \itemsEnd

    %--------High School--------
    \resumeEntry
        {Acton-Boxborough Regional High School}
        {2018 - 2022}
        {High School Diploma}
        {Acton, MA}

    \itemsBegin
        \item National Merit Finalist and Raytheon Scholar
        \item Unweighted 3.95 of 4.0 GPA; weighted 4.7 of 5.0 GPA, 35 ACT
        \item Advanced Placement (AP) Scholar with Distinction. AP Scores of 5 in AB Calculus, Biology, Computer Science A, Physics C: Mechanics, and Statistics
        \item One of only 369 students globally (0.47\%) to earn every point on the AP Computer Science A exam
        \item Dartmouth Book Award—presented to a junior for outstanding academic achievement and leadership
        \item National Honor Society, Swim and Dive Captain, Band Vice-President, Marching Band Section Leader, Junior and Senior Class Leader, Student Ambassador
    \itemsEnd

%----------- EXPERIENCE -----------
\section{Experience}

    %--------RTX 2024--------
    \resumeEntry
    {Software Engineer, Intern}
    {Summer 2024}
    {RTX}
    {Marlborough, MA}

    \itemsBegin
        \item Used Git and GitLab to develop Perl tooling for DevSecOps software pipeline. Jira administrator, created and configured projects for software teams, Groovy scripting for workflows. Jenkins administrator, updated and debugged CI/CD jobs. Validated and integrated C++ code changes into baseline.
    \itemsEnd

    %--------RTX 2023--------
    \resumeEntry
        {Software Engineer, Intern}
        {Summer 2023}
        {RTX}
        {Woburn, MA}

    \itemsBegin
        \item Worked on X-Band Radar software. Learned Ada language, ClearCase, Jenkins to support correcting software bugs and new development. Assisted in redevelopment of tool allowing better testing of capabilities of radar software. Participated in daily scrum, sprint planning and backlog refinement.
    \itemsEnd

    %--------Autobike--------
    \resumeEntry
        {Autonomous Bicycle Project Team}
        {2022 - Present}
        {Cornell University}
        {Ithaca, NY}

    \itemsBegin
        \item Software Lead. Reinforcement learning to determine optimal bicycle routing, Docker, Python. Optical flow and computer vision techniques to predict future occupancy grids, OpenCV.
    \itemsEnd

    %--------Tholyl--------
    \resumeEntry
        {Software Tester, Intern}
        {2022}
        {Tholyl Technologies}
        {Acton, MA}

    \itemsBegin
        \item Tested and reported bugs, provided insight into development of software product. Created and managed website.
    \itemsEnd

%-----------SELECTED ENGINEERING PROGRAMS-----------
\section{Selected Engineering Programs}


    %--------Hajim--------
    \resumeEntry
        {Hajim School of Engineering \& Applied Sciences Pre-College Intensive}
        {Summer 2021}
        {University of Rochester}
        {Virtual}

    \itemsBegin
        \item Attended competitive 20-student cohort three-week intensive studies program completing week-long modules in electrical and computer engineering, data science, and biomedical engineering.
    \itemsEnd

    %--------Luddy--------
    \resumeEntry
        {Luddy Pre-College Summer Computing \& Engineering Summer Program}
        {Summer 2021}
        {Indiana University, Luddy School of Informatics}
        {Virtual}

    \itemsBegin
        \item Attended a week-long pre-college exploratory program that covered topics such as intelligent sound-processing, microbiome gene sequencing, 3D modeling.
    \itemsEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}

    \itemsBegin
        \item \textbf{Languages}{: OCaml, C, ADA, Java, Python, JavaScript/HTML/CSS, Bash}
        \item \textbf{Frameworks}{: Svelte}
        \item \textbf{Developer Tools}{: Git, Docker, Jenkins, ClearCase}
    \itemsEnd

%-------------------------------------------
\end{document}
